Imminent range shifts in transboundary fish stocks challenge their management under climate change

### 2021-03-19 Scripts/Supplements.Rmd
typos insupplements

```{r toeFigureS4, eval = T,  echo = F, fig.width=4, fig.height=4, fig.cap =  "Average Time  of Emergence and standar dviation for a 64% confidence treshold  (purple) and a 98% confidence teshold (yellow)"}

@@

```{r toeFigureS5, eval = T,  echo = F, fig.width=4, fig.height=4, fig.cap =  "Distribution of Stock Share Ratio percentage change by the early (2021-2040) and middle (2040-2060) 21st centurury relative to today (1951-2005)"}

@@

```{r toeFigureS6, eval = T,  echo = F, fig.width=9, fig.height=12, fig.cap =  "Changes in Stock Share Ration by 2050 (2041-2060) relative to 1951-2005. Lines represent the average gain of transboundary stock share ratio with srrows going from the losing EEZ (point) to the winner (arrowhead). Polygons represent the percentage of initial species that will see a shift. Panel B zooms in to specific areas shown in grey boxes of A.", fig.scap="Changes in Stock Share Ration by 2050 (2041-2060) relative to 1951-2005.", out.extra=''}

>>>>

```{r toeFigureS4, eval = T,  echo = F, fig.width=4, fig.height=4, fig.cap =  "Average Time of Emergence and standard deviation for a 64% confidence threshold (purple) and a 98% confidence threshold (yellow)"}

@@

```{r toeFigureS5, eval = T,  echo = F, fig.width=4, fig.height=4, fig.cap =  "Distribution of Stock Share Ratio percentage change by the early (2021-2040) and middle (2040-2060) 21st century relative to today (1951-2005)"}

@@

```{r toeFigureS6, eval = T,  echo = F, fig.width=9, fig.height=12, fig.cap =  "Changes in Stock Share Ration by 2050 (2041-2060) relative to 1951-2005. Lines represent the average gain of transboundary stock share ratio with arrows going from the losing EEZ (point) to the winner (arrowhead). Polygons represent the percentage of initial species that will see a shift. Panel B zooms in to specific areas shown in grey boxes of A.", fig.scap="Changes in Stock Share Ration by 2050 (2041-2060) relative to 1951-2005.", out.extra=''}
